Ground state energy of diatomic molecules\\ in the Quantum Drude Oscillator model

### 2022-06-25 paper/main.tex
minor

@@

>>>>

    \begin{figure}[h!]
        \centering
            \includegraphics[scale=0.33]{plus_minus_coefs}
            \caption{\label{fig:coefs} Intersection loci of $c_{20}$ and $d_{20}$ with the $z=0$ plane}
    \end{figure}

@@

\section{Atomic data}

    We collect here the QDO parameters obtained in \cite{PhysRevB.87.144103}.

    \begin{table}[h!]
    \caption{\label{tab:atomic_data} Parameters for QDOs (in a.u.)}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        & $\omega$ & $m$ & $q$ \\
        \hline
        H  & 0.4273 & 0.6099 & 0.7080 \\
        Li & 0.0687 & 1.2545 & 0.9848 \\
        K  & 0.0630 & 0.8101 & 0.9670 \\
        Rb & 0.0603 & 0.7343 & 0.9274 \\
        Cs & 0.0531 & 0.6939 & 0.8950 \\
        He & 1.0187 & 0.5083 & 0.8532 \\
        Ne & 1.2965 & 0.3491 & 1.2494 \\
        Ar & 0.7272 & 0.3020 & 1.3314 \\
        Kr & 0.6359 & 0.2796 & 1.3741 \\
        Xe & 0.5152 & 0.2541 & 1.3570
    \end{tabular}
    \end{ruledtabular}
    \end{table}
